---
title: "p8105_hw1_yy3564"
author: "Yonghao YU"
date: "2024-09-17"
output: html_document
---
## Question 1
```{r}
# First, I load the dataset
data("penguins", package = "palmerpenguins")

```
# Then I use inline R code to write a short description
The name of the dataset is called penguins, the name of each column is `r names(penguins)`.             
The size of the dataset is `r nrow(penguins)` rows and `r ncol(penguins)` columns.                      
The mean fipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`.



```{r}
# After that I import the library and draw the scatterplot required!
library(tidyverse)
plotrequired = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(
    x = "Bill Length",
    y = "Flipper Length",
    title = "Scatterplot of Flipper Length and Bill Length"
  )
plotrequired
# Then I save the plot I have produced!
ggsave(filename = "scatterplot_penguins.png", plot = plotrequired)
```

## Question 2

```{r}
# Set the random seed and load the tidyverse package
set.seed(200)
library(tidyverse)

# First, create a random sample of size 10
sample = rnorm(10)

# Second, create a logical vector
logical = sample > 0

# Third, create a character vector
character = paste("Value", 1:10)

# Last, create a factor vector
factor = factor(sample(c("Level 1", "Level 2", "Level 3"), 10, replace = TRUE))

# Combine them into one data frame
data_frame = data.frame(
  Sample = sample,
  Logical = logical,
  Character = character,
  Factor = factor
)

# Display the data frame
print(data_frame)

```
Then calculate the mean for each columns one by one to check whether there are any problems during the calculations!

```{r}
Sample_mean = mean(data_frame %>% pull(Sample))
Sample_mean
```
```{r}
Logical_mean = mean(data_frame %>% pull(Logical))
Logical_mean
```

```{r}
Character_mean = mean(data_frame %>% pull(Character))
Character_mean
```

```{r}
Factor_mean = mean(data_frame %>% pull(Factor))
Factor_mean
```
When I print out these values, it shows obviously that the random sample and logical vector work and the charactor vector and the factor vector do not work!!!

```{r}
# Explicitly convert variables to numeric using pull function
numeric_logical = as.numeric(data_frame %>% pull(Logical))
numeric_character = as.numeric(data_frame %>% pull(Character))  
numeric_factor = as.numeric(data_frame %>% pull(Factor))
```
```{r}
# not checking the outputs 
# numeric_logical
# numeric_character
# numeric_factor
```

Logical to Numeric: Converting TRUE to 1 and FALSE to 0, then take the mean of numerous 0 and 1!!!!!

Character to Numeric:  Converting makes all entries NA because the strings can't be converted to numbers!!!!!

Factor to Numeric: Converting the factor levels to underlying integer, which allows for mean calculations but it is meaningless because it is just some meaningless numbers and it does not have the original categorical interpretation anymore!!!!!